\newglossaryentry{glos:passivechannels}{
    name={passive channels},
    description={\newline 
        TODO
    }
}

\newglossaryentry{glos:activechannels}{
    name={active channels},
    description={\newline 
        TODO
    }
}

\newglossaryentry{glos:ionchannels}{
    name={ion channels},
    description={\newline 
        Proteins in the lipidbilayer that allows ion flow through the cell
        membrane.
    }
}

\newglossaryentry{glos:ionpumps}{
    name={ion pumps},
    description={\newline 
        TODO
    }
}

\newglossaryentry{glos:mempot}{
    name={membrane potential},
    description={\newline 
        The electrical potenial across the neuron
        cell membrane
    }
}

\newglossaryentry{glos:respot}{
    name={resting membrane potential},
    description={\newline 
        Also referred to as resting potential. 
        The steady state potential when the neuron is not receiving any current input.
        Usually around -65 mV in reference to the the surrounding environment.
    }
}

\newglossaryentry{glos:extcell}{
    name={extracelluar},
    description={\newline 
        Space outside the cell.
    }
}

\newglossaryentry{glos:intcell}{
    name={intracellular},
    description={\newline 
        Space inside the cell. Contains cytoplasm.
    }
}

\newglossaryentry{glos:lipidbilayer}{
    name={lipid bilayer},
    description={\newline 
        TODO
    }
}

\newglossaryentry{glos:regspike}{
    name={regular spiking},
    description={\newline Often compared to fast spiking.}
}

\newglossaryentry{glos:fastspike}{
    name={fast spiking},
    description={\newline A short durtion extracelluar spike.}
}
